### 2014-12-30 paper_10_intro.tex
software analytics
continuing work on lit review

\subsection{COCOMO}
    Constructive Cost Model (COCOMO) is a software cost estimation model created
    by Boehm \cite{Boehm1981}.  It combines future project characteristics
    with historical project data to create a regression model to estimate the 
    cost of a software project.  The original version developed in 1981 was
    focused on mainframe and batch processing.  An unpdated version, named
    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
    development practices such as desktop development, off the shelf components,
    and code reuse.  COCOMO provides a nice algorithm for making decisions
    regarding building or buying software products.  It does not provide 
    an algorithms to review past performance of estimates and modify the
    algorithm accordingly.  COCOMO II can be a useful tool for an SDO,
    but it only provides an estimate and not an evaluation of the actual
    performance.

\subsection{PREVIOUS SOFTWARE SCORING ATTEMPTS }

@@

\subsubsection{SOFTWARE ANALYTICS}
See also \cite{Buse2010}.  There is a subsection named
software development analytics \cite{Menzies2012}.

>>>>

\subsection{PREVIOUS SOFTWARE EVALUATION ATTEMPTS }

@@

\subsubsection{SOFTWARE ANALYTICS}
What is software analytics?
See also \cite{Buse2010}.

\textit{Software Development Analytics} is a subfield of software analytics 
\cite{Menzies2012}.  It focuses on the analytics of the development of software, not
the overall performance of the software.

\cite{Marcus2010}

\subsubsection{COCOMO}  
    Constructive Cost Model (COCOMO) is a software cost estimation model created
    by Boehm \cite{Boehm1981}.  It combines future project characteristics
    with historical project data to create a regression model to estimate the 
    cost of a software project.  The original version developed in 1981 was
    focused on mainframe and batch processing.  An unpdated version, named
    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
    development practices such as desktop development, off the shelf components,
    and code reuse.  COCOMO provides a nice algorithm for making decisions
    regarding building or buying software products.  It does not provide 
    an algorithms to review past performance of estimates and modify the
    algorithm accordingly.  COCOMO II can be a useful tool for an SDO,
    but it only provides an estimate and not an evaluation of the actual
    performance.

### 2014-12-30 paper_20_sdo.tex
adding material that had been removed for the proposal
fixed Schedule chapter problem starting to work on SEMAT section
continuing work on lit review

    \subsubsection{AGILE}
        Agile software development has arisen due to the inability
        of the waterfall and other models to adjust to changes during the 
        development cycle.  
        Agile software development is a group of SDLC models that operate
        under the influence of the following four key principles \cite{Beck2001}.
        \begin{enumerate}
            \item Individuals and interactions over processes and tools
            \item Working software over comprehensive documentation
            \item Customer collaboration over contract negotiation
            \item Responding to change over following a plan
        \end{enumerate}
        Agile does not specify an implementation, but
        some specific models of agile SDLC are:
        eXtreme Programming, Scrum, Lean, Kanban and others 
        \cite{Moniruzzaman2013, Hibbs2009}.  Agile models 
        are very popular in many of today's software development
        organizations because the models work well for dynamic
        quickly changing applications such as web-based applications.

@@

%\subsection{Data-Driven Software Engineering}
%Data Driven Software Engineering not Data Driven Software Development

%Check these book \cite{Jones2009, Jones1996, Lee2003}. This might be similar
%to process mining \cite{vanderAalst2012}.

>>>>

    \subsubsection{AGILE}
        Agile software development has arisen due to the inability
        of the waterfall and other models to adjust to changes during the 
        development cycle.  
        Agile software development is a group of SDLC models that operate
        under the influence of the following four key principles \cite{Beck2001}.
        \begin{enumerate}
            \item Individuals and interactions over processes and tools
            \item Working software over comprehensive documentation
            \item Customer collaboration over contract negotiation
            \item Responding to change over following a plan
        \end{enumerate}
        Agile does not specify an implementation, but
        some specific models of agile SDLC are:
        eXtreme Programming, Scrum, Lean, Kanban and others 
        \cite{Moniruzzaman2013, Hibbs2009}.  Agile models 
        are very popular in many of today's software development
        organizations because the models work well for dynamic
        quickly changing applications such as web-based applications.
        Startups have largely adopted the Lean methodology for its
        ability to identify a minimum viable product\footnote{
        A \textit{minimum viable product} is a reduced version of software
        that contains only the bare minimum functionality required to meet
        the requirements.}
        and reduce the time to market \cite{Giardino2014}.

@@

Check these book \cite{Jones2009, Jones1996, Lee2003}. This might be similar
to process mining \cite{vanderAalst2012}.
